Meta-analysis

### 2020-09-02 04_MetaAnalysis.Rmd
Edits and treatment effects table for publication

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               lme4,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp)

@@

> Which spray management scenario provides the greatest yield protection from powdery mildew.

@@

   - We will test spray management (our treatment)

@@

For the first grain yield meta-analysis, we'll use the `metafor` package [@Viechtbauer2010].

To do a ARM based model we will use the package `metafor`.
We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.

@@

```{r PM_Mv_Contrast}
source("R/simple_summary.R")
summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
contrast_Ssum <- simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
contrast_Ssum
```

@@

```{r metafor_results}
results_AI <- data.frame(cbind(PM_mv$b,
                               PM_mv$ci.lb,
                               PM_mv$ci.ub))

efficacy <- as_tibble(results_AI)
efficacy$Treatment <-
   factor(c(

       "control",
      "Early",
      "Recommended",
      "Recommended_plus",
      "Late",
      "Late_plus"
   ))

efficacy$se <- PM_mv$se
colnames(efficacy) <-
   c("Mean", "CIs_lower", "CI_upper", "Treatment", "SE")
efficacy
```

```{r metafor_plot}
YieldContrasts <- efficacy %>%
   filter(Treatment != "control") %>% 
   mutate(Treatment = factor(Treatment, levels = rev(
      c(

         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()

YieldContrasts
```

@@

```{r Save_meta_data, eval=FALSE}
save(efficacy, PM_MB_dat, PM_mv, YieldContrasts, contrast_Ssum, 
     file = here("cache/Meta-analysisData.Rdata"))
```

>>>>

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp)

@@

> When, in relation to PM establishes in the crop, should farmers begin spraying mungbean to mitigate yield loss: before PM establishing,  immediately after first sign of PM establishing, or after PM has become established in the crop.

A secondary question to this aim is: given the time at which the first spray occurred is a second spray provide worthwhile yield protection.

@@

   - We will investigate the effect size of our treatment - spray management,

@@

For the first grain yield meta-analysis will be an ARM based model using the `metafor` package [@Viechtbauer2010].

We are using the `spray_management` variable as a moderator and an interactive term to the `trial` random variable.

@@

```{r metafor_results}

k5 <- as.data.frame(table(PM_MB_dat$trial, PM_MB_dat$spray_management)) %>%
   filter(Freq !=0)%>%
   group_by(Var2)%>%
   summarise(n())%>%
   pull()

results_mv <- data.frame(N = PM_mv$g.levels.k,
                         k = k5,
                         Effect = round(PM_mv$b,4),
                         se = round(PM_mv$se,4),
                         CI_lower = round(PM_mv$ci.lb,4),
                         CI_upper = round(PM_mv$ci.ub,4),
                         z_val = round(PM_mv$zval,4),
                         p_val = reportP(PM_mv$pval,AsNumeric = TRUE),
                         row.names = c("Intercept",
                                       "$Early_{single}$",
                                       "$Recommended_{single}$",
                                       "$Recommended_{plus}$",
                                       "$Late_{single}$",
                                       "$Late_{plus}$"))

colnames(results_mv)[c(1:4,6:9)] <- c("Treatment","$N$", "$k$","$\\mu$","$CI_{L}$","$CI_{U}$", "$Z$","$P$")

kable(results_mv[,2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Mean effect size of five spray schedule treatments on mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia. Effect sizes were estimated from the network meta-analysis of data obtained from grey literature reports. Intercept indicates the mean of the no spray control and the treatments show the mean difference to the intercept")

```{r metafor_plot}
results_mv %>%
   filter(Treatment != "control") %>% 
   mutate(Treatment = factor(Treatment, levels = rev(
      c(

         "Early",
         "Recommended",
         "Recommended_plus",
         "Late",
         "Late_plus"
      )
   ))) %>%
   ggplot(aes(Treatment, `$\\mu$`)) +
   geom_hline(
      yintercept = seq(-0.05, 0.3, by = 0.05),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_hline(yintercept = 0) +
   geom_point(aes(size = 1 / se), shape = 15) +
   geom_linerange(aes(ymin = `$CI_{L}$`, ymax = `$CI_{U}$`)) +
   coord_flip()+
   ggtitle("Mean spray schedule effect sizes\nand 95% confidence intervals")

Lets investigate the treatment contrasts

```{r PM_Mv_Contrast}
source("R/simple_summary.R") #function to provide a table that includes the treatment names in the contrasts
summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none"))
contrast_Ssum <- simple_summary(summary(glht(PM_mv, linfct=cbind(contrMat(rep(1,6), type="Tukey"))), test=adjusted("none")))
contrast_Ssum
```

@@

@@

```{r Save_meta_data, eval=FALSE}
save(efficacy, PM_MB_dat, PM_mv, contrast_Ssum, 
     file = here("cache/Meta-analysisData.Rdata"))
```
